A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-04 ECCV/paper.tex
Incorporated Michael's changes

\begin{abstract}
This paper describes the design and evaluation of a binary fiducial marker
for use with low-cost quadcopters.  Fiducial markers are commonly placed
in environments to provide a reliable and unique marker conducive for
tracking and recognition.   For quadcopter applications, fiducials are
typically used for evaluating planning algorithms by allowing ground truth
positions in the scene to be detected from the quadcopter's camera. Quadcopters,
however, are subject to quick and unstable motions that can cause significant motion
blur that severely affects the detection rate of existing fiducial markers.
This motivated us to design a fiducial that is robust to motion blur. Our design
uses a series of concentric circles with the observation is that the direction
perpendicular to the motion blur direction will be unaffected by the blur and
therefore still be recognizable.  We detail the design and
detection algorithm for our fiducial and show that our marker can significantly
outperform existing fiducial markers in scenes captured with a quadcopter.
\keywords{Fiducials, Tracking, Detection using Blur}
\end{abstract}

@@

The recent availability of low-cost quadcopters has help to fuel significant efforts in
research focused on Unmanned Aerial Vehicles.  Navigation and planning of
these vehicles is typically performed using onboard inertial sensors and/or
vision based modules that uses visual cues in the real world\cite{Davison:2007}. 
However, to evaluate the effectiveness of navigation methods, artificial
fiducial markers are commonly introduces into the environment to provide
additional information that often serves for ground-truth
measurements(e.g.\cite{Bosnak:2012,Lim09,Klopschitz:2007})

In order to be effective, fiducial markers (or simply called, fiducials) need
to be easily detected in the scene.  There are various existing commonly
used fiducial markers 
\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}.
These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric features arranged in unique spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
seen from a quad-copter.  One problem, however, is that low-cost quadcopters
often exhibit very quick and erratic motion.  These fast physical movements
results in motion blur in the quadcopters onboard camera.  Such motion blur has an adverse effect the
recognition of fiducial  markers.  This can be seen in Figure
\ref{fig:teaser}(b) where the ARTag cannot be recognized. This is not too surprising as most
fiducials are not explicitly designed to handle motion blur.  Compounding this
problem is the common problem of dropped video frames from the quadcopters
wireless communication module.   This means that no only is blurring
introduced, but there may be large discontinuities in the patterns position due
to missing video frames that makes tracking challenging.

To address this problem, propose a fiducial design that is robust to motion
blur and drastic drastic change in its position in successive frames.  Our
design is based on concentric circles as shown in Figure \ref{fig:fiducials}. 
The design is based on the observation that motion blur from a quadcopter tends
to be linear in nature.  As such, when our code is blurred, there is no blur in
the direction perpendicular to the direction of motion.   This allows the
signature of the fiducial to remain intact in any direction.  In addition, by
using concentric rings, we can treat them as bits allowing us to encode us
different fiducial identifiers.  As far as we are aware, this is the first work
to design a blur resistant marker.   Our experiments show that this design can
significantly outperform existing codes in the face of motion blur.

@@

\begin{figure}
\includegraphics[width=\linewidth]{teaser.pdf}
\caption{Figure showing experimental setup and comparison of
output of ALVAR\cite{alvar} (for detecting ARTag) versus output of our
algorithm, in normal and blurred scene. (b) clearly shows that ALVAR is not
able to detect ARTag in blurred image while our algorithm can detect our
fiducial in blurred image (d)}
\label{fig:teaser}
\end{figure}

@@

@@

\textbf{Fiducials} :- Some of fiducial designs are shown in Figure
\ref{fig:previous_work}.

\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}
\end{figure}

Initially there were attempts to design a fiducial embedded with two
dimensional barcode inside a rectangular grid. One of the examples of such fiducial is,
ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality(AR) system. 
Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit to find
the pose in video based AR conferencing system. Many AR applications used
ARToolkit due to its simplicity and efficiency.

@@

There were also attempts to use circular patterns instead of rectangular, as
the projective transformation of circles, i.e., conics, are invariant with
respective to point of view of camera\cite{runetag11}. Also, such patterns are
mostly distinguishable from background and generally can not be missed.

Concentric rings are reportedly used first by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
black and white rings\cite{concentric} to increase possible number of fiducials.
These multicolor rings are used in wide area tracking in large scale
applications.

Naimark et al. \cite{NaimarkF02} have combined concentric rings and 2D bar code
in their fiducial named, Circular Data Matrix. It was beneficial in terms of
easy detection of fiducial as well as more number of fiducial patterns.

All of these fiducials are not recognizable under occlusion.
Bergamasco et al. \cite{runetag11} have divided fiducial into number of
circular dots, and arranged them in circular fashion, named as RUNE-Tag.
RUNE-tags are reportedly detectable even if 50\% of fiducial area is occluded.
Bergamasco et al. have developed another fiducial, named as Pi-Tag
\cite{Pitag13}, using cross-ratio concept. As cross-ratio is projective
invariant, the detection of Pi-tag is easier than other tags. Also, compared
to RUNE-tag, it uses remarkably less number of circular dots (12 dots instead of
minimum of 43 dots), still recognisable under occlusion.

@@

\textbf{Tracking}:-
Fiducial detection in video may be considered as tracking problem where tracked
object is fiducial itself. Visual tracking plays an important role in
surveillance, robotics, human computer interaction, and medical
imaging\cite{Yilmaz:2006}. Yilmaz et al.\cite{Yilmaz:2006} have done survey of
various tracking methods.

Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02}
\cite{Mei:2009} ) assume image sequence to be blur free. But in reality, motion
blur is inherent part of most of the videos. Wu et al.\cite{Wu:2011} have
developed BLUr-driven Tracker (BLUT) framework for tracking motion-blurred
targets. BLUT is based on the observation that although motion blurs degrade
the visual features of the target, they at the same time, provide useful cues
about the movements to help tracking.

BLUT framework successfully tracks blurred target when there is uniform motion
and the position of tracked object does not change drastically in successive
frames. But in our case, due to frequently dropping of intermediate frame, this
criterion may not be satisfied.

@@

Before we detail the design of our fiducial, we examine the performance of two
popular fiducials under motion blur that have different designs. Specifically,
we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13}.

We scaled down ARTag as well as PiTag fiducial to size 150x150.  Then, we
blurred both fiducials at various orientations using different scales.
Figure \ref{fig:artag_pitag} shows sample blurred AR Tag and Pi-Tag. Finally, we
tried to detect ARTag using ALVAR library\cite{alvar} and Pi-Tag using\cite{ros_pitag}.
Figure \ref{fig:artag_pitag} shows ARTag and Pi-tag blurred with various blur
scales at different orientation. Table in the left side of Figure
\ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
markers at various blur scales. Table clearly indicates that both fiducial
markers can not handle large amount of motion blur.

\begin{minipage}[h!]{\textwidth}
\centering
 \begin{minipage}{0.7\textwidth}
\includegraphics[width=\linewidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
\end{minipage}
\begin{minipage}{0.25\textwidth}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\textwidth}{|Y|Y|Y|}
\cline{1-3}
\tiny{Blur} & \multicolumn{2}{c|}{\tiny{Recognition Rate}} \\\cline{2-3}
 \tiny{Scale}& \tiny{AR Tag} &	\tiny{Pi-Tag} \\ \cline{1-3}
\tiny{15} & \tiny{100} & \tiny{100} \\ \cline{1-3}
\tiny{30} & \tiny{0} & \tiny{100} \\  \cline{1-3}
\tiny{35} & \tiny{0} & \tiny{19} \\ \cline{1-3}
\tiny{50} & \tiny{0} & \tiny{0} \\ \cline{1-3}
\end{tabularx}
\end{minipage}
\label{fig:artag_pitag}
\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
scales at different orientation. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations. Table clearly indicates that both fiducial markers can not handle
large motion blur.}
\end{minipage}

@@

From Figure \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
fails when blur scale is more than 15. The reason behind this is, Pi-tag
detection is based on Ellipse detection which will fail in the presence of
significant amount of blur. So, ellipse detection may not be the efficient way
to detect circular patterns under blur.
\end{comment}
We have designed a fiducial that may be thought of as a binary code.  It
contains concentric white rings of equal widths on a black background with a
blurred border. The outermost and innermost rings represent the start and end
of the code and is embedded in the fiducial; these are not considered part of
the code itself. The binary code is represented by the presence (or absence) of
rings between ``marker'' rings.

@@

Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amount of blur.   In particular, we assume that scene motion
blur be modelled locally as a linear motion blur \cite{Moshe:2003,Moshe:2004}. 
Under this assumption, scene content perpendicular to the blur direction is 
unaffected by the blur.  Because of our circular design, this means the
perpendicular direction can be observed as a unblurred linear pattern.  Figure
\ref{fig:blur_direction} shows an example with various motion directions.

@@

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\label{fig:overall_flow}
\end{figure}

@@

\section{Experimental Validation}
We have implemented\footnote{Code as well as experimental data will be made
online soon} our algorithm in C++ using OpenCV library.
Our code was run on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.

Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Figure
\ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
around 0.3 seconds and can handle three to four frames per second.

@@

\subsubsection{Comparison with BLUT}
We have used sample image sequence (consisting of 20 frames) to test the
performance of BLUT\cite{Wu:2011} and compare it with our result on the same
image sequence. From Figure \ref{fig:BLUT_output}, it can be inferred that BLUT
is able to track the fiducial when the position of fiducial does not change too
much in successive frames. Also, it can be seen that, once BLUT looses the
track of the fiducial, it is not able to recover from that. But, our algorithm
is able to track the fiducial irrespective of the change in the position of the
fiducial in the image as shown in Figure \ref{fig:our_output}.

>>>>

\begin{abstract}
This paper describes the design and evaluation of a binary fiducial marker
for use with low-cost quadcopters.  Fiducial markers are commonly placed
in environments to provide a uniquely identifiable object in the scene.
For quadcopter applications, fiducials are
typically used for evaluating planning algorithms by allowing ground truth
positions in the scene to be detected from the quadcopter's camera. Quadcopters,
however, are subject to quick and unstable motions that can cause significant motion
blur that severely affects the detection rate of existing fiducial markers.
This problem motivated us to design a fiducial that is robust to motion blur.
Our proposed fiducial design uses concentric circles with the observation that the direction perpendicular to the motion blur direction will be unaffected by the blur.  As a result,
the fiducial code along this direction is recognizable.  The circular design allows this to
  work for all motion blur directions.  We detail the design and
detection algorithm for our fiducial and show that our marker can significantly
outperform existing fiducial markers in scenes captured with a quadcopter.
\keywords{Fiducials, tracking, recognition under blur}
\end{abstract}

@@

The recent availability of low-cost quadcopters has help to fuel significant efforts in
research focused on unmanned aerial vehicles.  Navigation and planning of
these vehicles is typically performed using onboard inertial sensors and/or
vision based modules that uses visual cues in the real world~\cite{Davison:2007}.
However, to evaluate the effectiveness of navigation methods, artificial
fiducial markers are commonly placed into the environment to provide
additional information that serves for ground-truth
positional measurements (e.g.\cite{Bosnak:2012,Lim09,Klopschitz:2007}).

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene.  A variety of fiducial markers
have been proposed in the literature (e.g.~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric features arranged in predefined spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser}-top shows an example of the popular ARTag\cite{Fiala05} as
seen from a quadcopter.  A problem for existing fiducials is  that low-cost quadcopters
oftenexhibit very quick and erratic physical movements that
results in motion blur in the quadcopters onboard camera.  This motion blur has an adverse effect the  recognition of fiducial  markers.  This can be seen in Figure
\ref{fig:teaser}(top) where the ARTag cannot be recognized due to motion blur. This is not too surprising as most  existing fiducials are not explicitly designed to handle motion blur.

Compounding this problem is the additional issue of dropped video frames from the quadcopters
wireless communication module.   This means that not only is blurring
introduced, but there may be large discontinuities in the patterns position due
to missing video frames.  As we will show in Section 4, this latter problem makes it challenging to apply tracking algorithms that can exploit temporal coherence for determining
the fiducial positions.

\noindent{\textbf Contribution}~~To address these problems, we propose a
fiducial that is designed to be robust to motion blur.  Our design is based on
concentric circles as shown in Figure \ref{fig:teaser}-b.  The design is based
on the observation that motion blur from a quadcopter tends to be linear in
nature.  As such, when our code is blurred, there is no blur in the direction
perpendicular to the direction of motion.   This allows the signature of the
fiducial to remain intact in any direction.  In addition, by using concentric
rings, we can treat the presence or absence of a ring as a bit, allowing us to
assign an code to the marker.  Our experiments show that this design can
significantly outperform existing codes in the face of motion blur. As far as
we are aware, this is the first work to propose a blur resistant marker.

@@

\begin{figure}
\includegraphics[width=\linewidth]{teaser.pdf}
\caption{This figure show experimental setup and comparison of
output of ALVAR\cite{alvar} (for detecting ARTag) versus our blur resistant fiducial
in a normal and blurred scene. The scene contains two ARTags and our code.
(a) shows that the ARTag can be detected when the image has no blur. 
(b) shows that ARTags are no longer detectible due to the blur.
(c-d) show the same images in (a) and (b) where our code is being detected.}
\label{fig:teaser}
\end{figure}

@@

[MSB: related works still needs a couple more passes, I've left it as it.
as mentioned yesterday, we need to address the problems with the circular 
pattern design, this needs to be done in the same paragraph, not later as done now. ]

@@

\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 suitable for many environments that are not designed to be recognized under blur.}
 \label{fig:previous_work}
\end{figure}

\noindent{\textbf{Fiducials}}~Figure~\ref{fig:previous_work} shows several examples
of existing fiducial markers.  Many designs use a two dimensional barcode inside a rectangular grid. One of the examples of such fiducial is, ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality (AR) system. Kato et al.\cite{kato-artoolkit} have demonstrated the use of ARToolkit to find the pose in video based AR conferencing system. Many AR applications used
ARToolkit due to its simplicity and efficiency.

@@

There were also attempts to use circular patterns instead of rectangular, as
the projective transformation of circles, i.e., conics, are invariant with
respective to point of view of camera\cite{runetag11}. Also, such patterns are
more distinguishable from the background scene due to their unique design.

The use of concentric rings was used  by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
black and white rings\cite{concentric} to increase possible number of fiducials.
These multicolor rings are used in wide area tracking in large scale
applications.

Naimark et al. \cite{NaimarkF02} have combined concentric rings and 2D bar code
in their fiducial named, Circular Data Matrix. It was beneficial in terms of
easy detection of fiducial as well as being able to encode more unique IDs.

All of these fiducials are not recognizable under occlusion.
Bergamasco et al. \cite{runetag11} have divided fiducial into number of
circular dots, and arranged them in circular fashion, named as RUNE-Tag.
RUNE-tags are reportedly detectable even if 50\% of fiducial area is occluded.
Bergamasco et al. have developed another fiducial, named as Pi-Tag
\cite{Pitag13}, using the cross-ratio concept. As cross-ratio is projective
invariant, the detection of Pi-tag is easier than other tags. Also, compared
to RUNE-tag, it uses remarkably less number of circular dots (12 dots instead of
minimum of 43 dots), still recognisable under occlusion.

@@

\noindent{\textbf{Tracking}}~~Fiducial detection between successive video 
frames can be considered a tracking problem where the tracked object is fiducial itself.
There is a very large body of research dedicated to tracking and interested
readers are referred to~\cite{Yilmaz:2006} for a survey.

Most tracking methods( \cite{Ross:2008,Wu:2009,Perez02}
\cite{Mei:2009} ) assume the image sequence to be blur free. In reality, however,
motion blur in video sequences is often unavoidable. Wu et al.\cite{Wu:2011} have
developed BLUr-driven Tracker (BLUT) framework for tracking motion-blurred
targets. BLUT is based on the observation that although motion blurs degrade
the visual features of the target, they at the same time, provide useful cues
about the movements to help tracking.

The BLUT framework successfully tracks blurred target when there is uniform motion
and the position of tracked object does not change drastically in successive
frames. But as we will demonstrate in Section 4, the erratic motion from quadcopters as 
well as the problem of dropped video frames is beyond the current ability of such trackers.

@@

Before we detail the design of our fiducial, we examine the performance of two
popular fiducials under motion blur.  Specifically we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.

To simulate the appearance of the maker as seen by a quadcopter, 
we scaled down ARTag as well as PiTag fiducial to size 150x150. 
 Both fiducials are then blurred at various orientations with different blurs scales
(denoted in pixels).   The blur motion ranged from X to Y in magnitude, representing
small to significant moton blur.   Figure \ref{fig:artag_pitag} shows the visual appearance
of the blurred tags.   We then use try to detect the markers using the 
ALVAR library\cite{alvar} and Pi-Tag library\cite{ros_pitag}.
The table in the left side of Figure
\ref{fig:artag_pitag} shows the recognition rate (in percent) of two fiducial
markers at various blur scales under different orientation.   As we can see, the PiTag performance quickly diminished under small amounts of blur, however, at 40 motion blur, ARTag is recognition rate drops to less than 20\%.

\begin{minipage}[h!]{\textwidth}
\centering
 \begin{minipage}{0.7\textwidth}
\includegraphics[width=\linewidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
\end{minipage}
\begin{minipage}{0.25\textwidth}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\textwidth}{|Y|Y|Y|}
\cline{1-3}
\tiny{Blur} & \multicolumn{2}{c|}{\tiny{Recognition Rate}} \\\cline{2-3}
 \tiny{Scale}& \tiny{AR Tag} &	\tiny{Pi-Tag} \\ \cline{1-3}
\tiny{15} & \tiny{100} & \tiny{100} \\ \cline{1-3}
\tiny{30} & \tiny{0} & \tiny{100} \\  \cline{1-3}
\tiny{35} & \tiny{0} & \tiny{19} \\ \cline{1-3}
\tiny{50} & \tiny{0} & \tiny{0} \\ \cline{1-3}
\end{tabularx}
\end{minipage}
\label{fig:artag_pitag}
\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
scales at different orientation. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tag is significantly reduces due to blur.
For severe blur, detection is not possible.}
\end{minipage}

\subsection{Blur Resistent Fiducial}

@@

From Figure \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
fails when blur scale is more than 15. The reason behind this is, Pi-tag
detection is based on Ellipse detection which will fail in the presence of
significant amount of blur. So, ellipse detection may not be the efficient way
to detect circular patterns under blur.
\end{comment}

We have designed a fiducial that can be considered a binary code.  The design
uses concentric white rings of equal widths on a black background with a
blurred border\footnote{This design can be easily inverted to have a white background with white rings}. The outermost and innermost rings represent the start and end
of the code and is embedded in the fiducial.  The binary code is represented by the presence (or absence) of rings between ``marker'' rings.

@@

Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amounts of blur.   As previously mentioned, our approach works
 under the assumption that the motion blur on the camera mount on the quadcoptuer
 can be modelled as linear motion.  This assumption about the motion blur has been shown to be
 reasonable in prior works targeting camera motion blur (e.g.~\cite{Moshe:2003,Moshe:2004}).
Under this assumption, the scene content perpendicular to the blur direction is
unaffected by the blur.  Because of our circular design, this means the
perpendicular direction can be observed as a unblurred linear pattern.  Figure
\ref{fig:blur_direction} shows an example with various motion directions.

[MSB: You have to describe the algorithm here as discussed yesterday.  Please complete this
part.]
 We give a brief overview of our algorithm here and details to each step in the following. Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
process. Our detection algorithm has four steps.  First, we apply a Gabor filter on the camera frame, next . . .

@@

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow - [MSB: Details?  This is why I said this I didn't think this
was the updated version of the paper. We discussed this yesterday, you need details in all of your captions.] }
\label{fig:overall_flow}
\end{figure}

@@

\section{Experimental Validation}

[MSB: As discussed yesterday, in the table reporting the results you need to give the 
number of frames in tested video clip.  We may also need to comment on the
number of dropped frames if this is possible to get. We mentioned this in the
paper, but never mentioned this in the experimetal results.]

We have implemented our algorithm in C++ using OpenCV library.
Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
Source code and data sets in this paper will be made publicly available.

Our system has been tested several image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Figure
\ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
around 0.3 seconds and can handle three to four frames per second.

@@

\subsubsection{Comparison with BLUT}

We have used sample image sequence (consisting of 20 frames [MSB: This is inviting trouble, I can guarentee you this will likely get your paper rejected.]) to test the performance of BLUT\cite{Wu:2011} and compare it with our result on the same
image sequence. From Figure \ref{fig:BLUT_output}, it can be inferred that BLUT
is able to track the fiducial when the position of fiducial does not change too
much in successive frames. Also, it can be seen that, once BLUT looses the
track of the fiducial, it is not able to recover from that. But, our algorithm
is able to track the fiducial irrespective of the change in the position of the
fiducial in the image as shown in Figure \ref{fig:our_output}.
